```{r, echo=FALSE, include=FALSE}
## Get VERSION and create file names
ver <- sub(x = grep(x = readLines("DESCRIPTION"),
           pattern = "^Version: ",
           value = TRUE),
           pattern = "^Version: ", replacement = "")
pkg.name <- "Regrans_"
pkg.source <- paste0(pkg.name, ver, ".tar.gz")
pkg.win <- paste0(pkg.name, ver, ".zip")
```

# Regrans `r ver`

[![Build Status](https://travis-ci.org/rodrigosantana/Regrans.svg)](https://travis-ci.org/rodrigosantana/Regrans)

Segmented Linear Regression Models

## Introduction

Regrans was designed to fit segmented regression models.

## Download and install

### Linux/Mac

Use the `devtools` package (available from
[CRAN](http://cran-r.c3sl.ufpr.br/web/packages/devtools/index.html)) to
install automatically from the official Git repository:

```{r, eval=FALSE}
library(devtools)
install_github("rodrigosantana/Regrans")
```

Alternatively, download the package tarball: [`r pkg.source`][]
and run from a UNIX terminal (make sure you are on the container file
directory):

```{r, echo=FALSE, comment=NA}
cmd <- paste("R CMD INSTALL -l /path/to/your/R/library", pkg.source)
cat(cmd, sep = "\n")
```

Or, inside an `R` session:


```{r, echo=FALSE, comment=NA}
inst <- paste0("install.packages(", "\"", pkg.source, "\"", ", repos = NULL,\n",
               "                 lib.loc = \"/path/to/your/R/library\",\n",
               "                 dependencies = TRUE)")
cat(inst, sep = "\n")
```

Note that `-l /path/to/your/R/library` in the former and `lib.loc =
"/path/to/your/R/library"` in the latter are optional. Only use it if you
want to install in a personal library, other than the standard R
library.

### Windows

Download Windows binary version: [`r pkg.win`][] (**do not unzip
it under Windows**), put the file in your working directory, and from
inside `R`:

```{r, echo=FALSE, comment=NA}
instw <- paste0("install.packages(", "\"", pkg.win, "\"", ", repos = NULL,\n",
                "                 dependencies = TRUE)")
cat(instw, sep = "\n")
```

## Documentation

The reference manual in PDF can be found here: [Regrans-manual.pdf][]

## License

This package is released under the
[GNU General Public License (GPL) v. 3.0](http://www.gnu.org/licenses/gpl-3.0.html)

```{r, echo=FALSE, include=FALSE}
pkg.source.link <- paste0(
    "https://github.com/rodrigosantana/Regrans/blob/master/downloads/",
    pkg.source, "?raw=true")
pkg.win.link <- paste0(
    "https://github.com/rodrigosantana/Regrans/blob/master/downloads/",
    pkg.win, "?raw=true")
```

[`r pkg.source`]: `r pkg.source.link`
[`r pkg.win`]: `r pkg.win.link`
[Regrans-manual.pdf]: https://github.com/rodrigosantana/Regrans/raw/master/downloads/Regrans-manual.pdf
